---
title: Does the ZVI filter work in a selective or non-specific manner - Differential
  Abundance?
date: '`r Sys.Date()`'
output:
  bookdown::pdf_document2: 
    toc: FALSE
---

```{r setup, warning=FALSE, message = FALSE, echo = FALSE}
library(tidyverse)
library(git2r)
library(devtools)
library(knitr)
## Load required data files 
## dat <- readRDS("../data/input_data.RDS")
```

# Objective 

# Approach  
16S Differential abundance analysis - Using 16S data to look for OTUs enriched in ZVI and reclaimed water 
OTU level differential abundance analysis
Compare OTU list between edgeR and metagenomeSeq?

# Results  

# Summary

# Session information 

## Git repo commit information
```{r}
repo <- repository(path = "../")
last_commit <- commits(repo)[[1]]
```

The current git commit of this file is `r last_commit@sha`, which is on the `r branches(repo)[[1]]@name` branch and was made by `r last_commit@committer@name` on `r when(last_commit)`. The current commit message is `r last_commit@summary`. The repository is online at https://github.com/nate-d-olson/mgtst-pub  


## Platform Information
```{r}
s_info <- devtools::session_info()
print(s_info$platform)
```


## Package Versions
```{r}
s_info$packages %>% filter(`*` == "*") %>% select(-`*`) %>% 
      knitr::kable()
```
