---
title: "Does the ZVI filter work in a selective or non-specific manner - Diversity?"
date: '`r Sys.Date()`'
output:
  bookdown::pdf_document2: 
    toc: FALSE
---

```{r setup, warning=FALSE, message = FALSE, echo = FALSE}
library(tidyverse)
library(git2r)
library(devtools)
library(knitr)
## Load required data files 
## dat <- readRDS("../data/input_data.RDS")
```

# Objective 

# Approach  
Alpha diversity - evenness metric using shannon-better for 
Beta diversity analysis  - Using 16S is the overall community composition different between ZVI and reclaimed water - expectation is that if ZVI works in a specific manner that composition will be different, though differences in sequencing depth may bias the results. 
Test for differences using ANOSIM 

# Results  

## Beta diversity
Perform same analysis for the four different diversity metrics
1. using phyloseq object
2. select samples of interest  
select_sample(ps, samples_to_keep)

3. calculate distance 
Example code 
dist_mat <- distance(ps, method = i)

4. plot ordination
Example code 
ord <- ordinate(ps, method = "PCoA", distance = dist_mat)

plot_ordination(ps, ord, color= "Stage", title = "Bray Curtis PCoA") + theme_bw() + stat_ellipse()

5. use distance calculations for ANOSIM
anosim(dist_mat, grouping = factor(ps@sam_data$sample_code))

# Summary

# Session information 

## Git repo commit information
```{r}
repo <- repository(path = "../")
last_commit <- commits(repo)[[1]]
```

The current git commit of this file is `r last_commit@sha`, which is on the `r branches(repo)[[1]]@name` branch and was made by `r last_commit@committer@name` on `r when(last_commit)`. The current commit message is `r last_commit@summary`. The repository is online at https://github.com/nate-d-olson/mgtst-pub  


## Platform Information
```{r}
s_info <- devtools::session_info()
print(s_info$platform)
```


## Package Versions
```{r}
s_info$packages %>% filter(`*` == "*") %>% select(-`*`) %>% 
      knitr::kable()
```
