---
title: "Does ZVI lower microbial diversity?"
author: "Nate"
date: '`r Sys.Date()`'
output:
  bookdown::pdf_document2: 
    toc: FALSE
---

```{r setup, warning=FALSE, message = FALSE, echo = FALSE}
library(tidyverse)
library(git2r)
library(devtools)
library(knitr)
library(breakaway)
## Load required data files 
meta_df <- read_csv("../data/raw_data/zvi_meta.csv")
load("../cache/richness_df.RData")
```

# Objective 
Determine if ZVI filtration lowers microbial diversity.

# Approach  

- 16S Alpha diversity analysis - compare the diversity between ZVI filtered and reclaimed water. 
Test for differences using appropriate paired two sample test (may need to account for temporal sampling)

- Total abundance - if E. coli dominant, use E. coli MPN as abundance measurement

# Results  

### Alpha Diversity Analysis 

```{r rwZwAlphaTidy, echo = FALSE, message = FALSE}
richness_df <- richness_df %>% 
    rename(Sample_ID = sample_id) %>% 
    right_join(meta_df)
rw_v_zw <- richness_df %>% filter(Sample_Code %in% c("RW","ZW"))
```

```{r rwZwAlphaPlot, fig.cap = "Comparison of richness estimates between samples collected before and after ZVI filtration, RW and ZW sample types respectively."}
ggplot(rw_v_zw) + 
    geom_pointrange(aes(x = Sample_Code, y = est, 
                        ymin = lower, ymax = upper)) +
    scale_y_log10() + 
    theme_bw() + facet_wrap(~Collection_Date) + 
    labs(y = "Richness Estimate", x = "Sample Type")
```

### Alpha Diversity Significance Test
```{r rwZwAlphaStats}
sample_code <- rw_v_zw$Sample_Code

design_mat <- model.matrix(~ sample_code + 1)

colnames(design_mat) <- colnames(design_mat) %>% str_replace("sample_code","")
rw_v_zw_betta <- betta_random(chats = rw_v_zw$est, ses = rw_v_zw$seest, 
                              X = design_mat, groups = rw_v_zw$Collection_Date)
rw_rich <- rw_v_zw_betta$table[1,1] %>% round(0)
rw_se <- rw_v_zw_betta$table[1,2] %>% round(0)
zw_rich <- rw_rich + rw_v_zw_betta$table[2,1] %>% round(0)
zw_se <- rw_v_zw_betta$table[2,2] %>% round(0)
p_val <- rw_v_zw_betta$table[2,3]
rw_v_zw_betta$table
```

# Summary
Using breakaway betta model to test for differences in richness in samples collected before and after ZVI filtration. 
The `betta_random` model was used to account for paired samples with collection date as a random effect. 
While richness decreased after ZVI filtration (RW - `r rw_rich` $\pm$ `r rw_se`, ZW - `r zw_rich` $\pm$ `r zw_se` ), the change in richeness was not statistically significant, p = `r p_val`.

# Session information 

## Git repo commit information
```{r}
repo <- repository(path = "../")
last_commit <- commits(repo)[[1]]
```

The current git commit of this file is `r last_commit@sha`, which is on the `r branches(repo)[[1]]@name` branch and was made by `r last_commit@committer@name` on `r when(last_commit)`. The current commit message is `r last_commit@summary`. The repository is online at https://github.com/nate-d-olson/mgtst-pub  


## Platform Information
```{r}
s_info <- devtools::session_info()
print(s_info$platform)
```


## Package Versions
```{r}
s_info$packages %>% filter(`*` == "*") %>% select(-`*`) %>% 
      knitr::kable()
```

